Splitting It Up: The \pkg{spduration} Split-Population Duration Regression Package for Time-varying Covariates

### 2017-10-30 R Journal/beger-hill-metternich-minhas-ward.tex
resubmission to R journal
added DOIs, example code all works and is consistent with paper

\begin{example}
  bscoup$coup <- ifelse(bscoup$coup=="yes", 1, 0)
  bscoup <- add_duration(bscoup, "coup", unitID = "countryid", 
  +    tID = "year", freq = "year", ongoing = FALSE)
  Warning message:
  In attempt_date(data[, tID], freq) :
  Converting to 'Date' class with yyyy-06-30
\end{example}

@@

\begin{example}
  plot_hazard(loglog_model, main = "A")
\end{example}

@@

\begin{example}
  plot_hazard(loglog_model, xvals = c(1, 1, 10, 0.05), 
  +    zvals = c(1, 7, 8.64, 1, 1, 0.05, 0, 0), main = "B")
\end{example}

@@

\begin{example}
  plot(weib_model)
  plot(loglog_model)
\end{example}

@@

\begin{example}
  weib2_test_p   <- predict(weib_model2, newdata = coup_test)
  loglog2_test_p <- predict(loglog_model2, newdata = coup_test)
\end{example}

>>>>

\begin{example}
  bscoup <- add_duration(bscoup, "coup", unitID = "countryid", 
  +    tID = "year", freq = "year", ongoing = FALSE)
  Warning message:
  In attempt_date(data[, tID], freq) :
  Converting to 'Date' class with yyyy-06-30
\end{example}

@@

\begin{example}
  plot(loglog_model, type = "hazard", main = "A")
\end{example}

@@

\begin{example}
  plot(loglog_model, type = "hazard", xvals = c(1, 1, 10, 0.05), 
  +    zvals = c(1, 7, 8.64, 1, 1, 0.05, 0, 0), main = "B")
\end{example}

@@

\begin{example}
  plot(weib_model, lwd1 = 1, lwd2 = 1)
  title(main="Weibull")
  plot(loglog_model, lwd1 = 1, lwd2 = 1)
  title(main="Loglog")
\end{example}

@@

\begin{example}
  weib2_test_p   <- predict(weib_model2, newdata = coup_test, na.action = "na.omit")
  loglog2_test_p <- predict(loglog_model2, newdata = coup_test, na.action = "na.omit")
\end{example}
